---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## Creating a hexagon map of Tasmania

Tasmania is a state of Australia, it has one large land mass and several smaller islands.

### Data

We will use the Australian Bureau of Statistics' ESRI shape files to build our map.
Provided for convenience:

https://srkobakian.github.io/sugaRbag/articles/abs-data.html


Filtering for only Tasmanian areas.
The data set of Tasmanian Statistical Areas at level two has been provided as a package data set, `tas_sa2`.

### Centroids

Derive the central points of the provided polygons

```{r}
centroids <- create_centroids(tas_sa2, "SA2_5DIG16")
```

### Hexagon grid

To tesselate correctly, all the hexagons must be evenly spaced.

```{r}
grid <- create_grid(centroids = centroids, hex_size = 0.1, buffer_dist = 0.01, verbose = FALSE)
```

### Allocate areas

Each polygon centroid will be allocated to the closest available hexagon grid point.

```{r}

```



