---
title: "Vignette Title"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", message = FALSE
)
```

```{r}
library(tidyverse)
library(viridis)
```


The sugaRbag package can be downloaded directly from github:

```{r}
#devtools::install_github("srkobakian/sugaRbag")
library(sugaRbag)
```


## Creating a hexagon map of Tasmania

Tasmania is a state of Australia, it has one large land mass and several smaller islands.

### Data

We will use the Australian Bureau of Statistics' ESRI shape files to build our map.
Provided for convenience:

https://srkobakian.github.io/sugaRbag/articles/abs-data.html


Filtering for only Tasmanian areas.
The data set of Tasmanian Statistical Areas at level two has been provided as a package data set, `tas_sa2`.

### Centroids

Derive the central points of the provided polygons

```{r}
centroids <- create_centroids(tas_sa2, "SA2_5DIG16")
```

### Hexagon grid

To tesselate correctly, all the hexagons must be evenly spaced.

```{r}
grid <- create_grid(centroids = centroids, hex_size = 0.1, buffer_dist = 0.1)
```

### Allocate areas

Each polygon centroid will be allocated to the closest available hexagon grid point.
The capital cities data set will be used to preserve neighbourly relationships.

```{r}
hex_allocated <- allocate(centroids = centroids,
  hex_grid = grid,
  hex_size = 0.1, # same size used in create_grid
  filter_dist = 0.25,
  focal_points = sugaRbag::capital_cities,
  width = 30,
  id = "SA2_5DIG16", verbose = TRUE) # same column used in create_centroids
```


```{r}
h1 <- hex_allocated %>%
  group_nest(SA2_5DIG16) %>%
                mutate(hex = purrr::map(data, fortify_hexagon, hex_size = 0.1)) %>%
                unnest(data) %>% 
  unnest(hex) %>% left_join(., tas_sa2)

p1 <- fortify_sfc(tas_sa2)

ggplot(mapping = aes(fill = SA4_NAME16)) +
  geom_polygon(data = p1, aes(x=long, lat, group = group), alpha = 0.1) +
  geom_polygon(data = h1, aes(x=hexv_long, hexv_lat, group = SA2_5DIG16))
```



