---
title: "Tasmania"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tasmania}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  message = FALSE, 
  warning = FALSE,
  fig.height = 4,
  fig.width = 7)
```

The sugarbag package can be downloaded directly from github:

```{r sugarbag}
#remotes::install_github("srkobakian/sugarbag")
library(sugarbag)
```

```{r libraries}
library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
```


## Creating a hexagon map of Tasmania

Tasmania is a state of Australia, it has one large land mass and several smaller islands.

### Data

We will use the Australian Bureau of Statistics' ESRI shape files to build our map.
Provided for convenience on the package website:

https://srkobakian.github.io/sugarbag/articles/abs-data.html


The set has been filtered for only Tasmanian areas.
The data set of Tasmanian Statistical Areas at level two has been provided as a package data set, `?tas_sa2`.

### Centroids

The function create_centroids finds the central points of the polygons provided as an argument.

```{r centroids}
centroids <- create_centroids(tas_sa2, sf_id = "SA2_5DIG16")
```

### Hexagon grid

To tesselate correctly, all the hexagons must be evenly spaced.
This function creates a grid of possible locations for the polygons.

```{r grid}
grid <- create_grid(centroids = centroids, hex_size = 0.2, buffer_dist = 1.2)
```

### Allocate areas

Each polygon centroid will be allocated to the closest available hexagon grid point.
The capital cities data set will be used to preserve neighbourly relationships.

```{r allocation}
hex_allocated <- allocate(centroids = centroids,
  sf_id = "SA2_5DIG16",
  hex_grid = grid,
  hex_size = 0.2, # same size used in create_grid
  hex_filter = 10,
  focal_points = capital_cities,
  width = 30, verbose = TRUE) # same column used in create_centroids
```


```{r ggplot}
h1 <- hex_allocated %>%
  fortify_hexagon(hex_size = 0.2, sf_id = "SA2_5DIG16") %>%
  left_join(., tas_sa2) %>% mutate(poly_type = "hex")

p1 <- fortify_sfc(tas_sa2) %>% mutate(poly_type = "geo")

ggplot(mapping = aes(fill = SA4_NAME16)) +
  geom_polygon(data = p1, aes(x=long, lat, group = interaction(SA2_5DIG16,polygon)), alpha = 0.4) +
  geom_polygon(data = h1, aes(x=long, lat, group = interaction(SA2_5DIG16)))
```


```{r animation}
hex_anim <- h1 %>% 
  select(SA4_NAME16, SA2_5DIG16, 	
SA2_NAME16, long, lat, poly_type) %>% 
  left_join(p1 %>% distinct(SA2_5DIG16, polygon), by = "SA2_5DIG16")
geo_anim <- p1 %>% 
  select(SA4_NAME16, SA2_5DIG16, 	
SA2_NAME16, long, lat, polygon, poly_type)
anim_tas <- bind_rows(hex_anim, geo_anim) %>% left_join(homeless)

anim_tas %>% 
  ggplot(aes(x=long, y=lat, group = interaction(polygon, SA2_5DIG16))) +
  geom_polygon(aes(fill = SA4_NAME16)) +
  geom_polygon(data = geo_anim %>% select(-poly_type), fill = "grey40", alpha = 0.05) + 
  coord_equal() + 
  theme_void() + 
  guides(fill = guide_legend(title = NULL)) + 
  theme(legend.position = "bottom") +
  facet_wrap(~poly_type)
```

